\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-03-06 paper/eccv2020/sections/method.tex
Changed captured_diffuse figure titles.

Initial estimates $n'_\text{first}$ and $n'_\text{last}$ are set to the minimum
value in $\mathcal{E}$ and the maximum value, incremented by one bin. 
Then, we refine these estimates by selecting the closest bins that remain above
a threshold $\tau$ such that
\begin{equation}
    \begin{split}
        &\hat n_\text{first}=\min\{n : h[n] > \tau, h[n+1] > \tau,
            \cdots, h[n'_\text{first}] > \tau\}\\
        &\hat n_\text{last}=\max\{n : h[n'_\text{last}] > \tau,
    \cdots, h[n-1] > \tau, h[n] > \tau\}.
    \end{split}
\end{equation}
The remaining ambient counts are discarded by setting the recorded counts to
zero for all bins where \edit{$n < n_\text{first}$} and $n > n_\text{last}$. We use 
$\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.

>>>>

Initial estimates $n'_\text{first}$ and $n'_\text{last}$ are set to the minimum
value in $\mathcal{E}$ and the maximum value, incremented by one bin. 
Then, we refine these estimates by selecting the closest bins that remain above
a threshold $\tau$ such that
\begin{equation}
    \begin{split}
        &\hat n_\text{first}=\min\{n : h[n] > \tau, h[n+1] > \tau,
            \cdots, h[n'_\text{first}] > \tau\}\\
        &\hat n_\text{last}=\max\{n : h[n'_\text{last}] > \tau,
    \cdots, h[n-1] > \tau, h[n] > \tau\}.
    \end{split}
\end{equation}
The remaining ambient counts are discarded by setting the recorded counts to
zero for all bins where \edit{$n < \hat n_\text{first}$} and $n > \hat n_\text{last}$. We use 
$\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.
